Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-04 report/report.tex
Update todo
Delimitations section

@@

\section{Problem constraints}

In this study, when working with OSM geodata, the following assumptions have been made about the dataset to reduce the size of the problem domain:

\begin{enumerate}
    \item The program will not handle terrain features and altitude. It will be assumed that the road mesh can be projected on a flat 2D surface without feature intersection.
    \item It will be assumed that the city map consists of only arterial (primary) roads, secondary roads and footpaths.
    \item It will be assumed that the OSM dataset represents all roads as simple polylines, and building footprints as simple connected polygons. Any other features (such as squares, which are roads represented as polygons) will be omitted from the dataset.
    \item The road network is assumed to be a 2D simple graph. This means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the dataset. Any self-connected nodes will also be eliminated from the dataset.
\end{enumerate}

@@

% Onsdag:
% TODO: Delimitations in Introduction, after RQ
% TODO: Move: 2.1.1: Accuracy criteria that will not be focused on -> Delimitations

% Torsdag:
% TODO: Mention that positional accuracy will be the focus early on
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Split up introduction, more subsections
% TODO: Go over all images, add a line about their origins

>>>>

\section{Delimitations}

in this study, when working with osm geodata, the following assumptions have been made about the dataset to reduce the size of the problem domain:

\begin{enumerate}
    \item the program will not handle terrain features and altitude. it will be assumed that the road mesh can be projected on a flat 2d surface without feature intersection.
    \item it will be assumed that the city map consists of only arterial (primary) roads, secondary roads and footpaths.
    \item it will be assumed that the osm dataset represents all roads as simple polylines, and building footprints as simple connected polygons. any other features (such as squares, which are roads represented as polygons) will be omitted from the dataset.
    \item the road network is assumed to be a 2d simple graph. this means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the dataset. any self-connected nodes will also be eliminated from the dataset.
\end{enumerate}

@@

@@

% Torsdag:
% TODO: Mention that positional accuracy will be the focus early on
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Split up introduction, more subsections
% TODO: Delimitations in Introduction, after RQ
% TODO: Move: 2.1.1: Accuracy criteria that will not be focused on -> Delimitations
